---
title: "OHDSI ECMO: tables and plots"
output:
  word_document:
    reference_docx: word-styles-reference-01.docx
editor_options: 
  chunk_output_type: console
---


```{r setup , include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning=FALSE,
                      fig.align = "center", 
                      dev = "png",
                      cache = FALSE)
```

```{r}
library(knitr)
library(flextable)
library(officer)
library(png)
 

# folders -----
folder.cohortDiagnostics.results<-"C:/Users/Ed/Dropbox/OHDSI/covid/ECMO/GitHub/CharacterisationAndPlpECMO/network results/cohort diagnostics"
folder.table_1_output<-"C:/Users/Ed/Dropbox/OHDSI/covid/ECMO/GitHub/CharacterisationAndPlpECMO/network results/table 1 output"
working.figs_tables<-"C:/Users/Ed/Dropbox/OHDSI/covid/ECMO/GitHub/CharacterisationAndPlpECMO/network results/working figures and tables"
final.figs_tables<-"C:/Users/Ed/Dropbox/OHDSI/covid/ECMO/GitHub/CharacterisationAndPlpECMO/network results/final figures and tables"

# names ----
names<-c("Results_CUIMC", "Results_optumDod",
         "Results_hospital_charge_datamaster", "Results_CCAE", "Results_MDCD", "Results_Panther",
         "Results_Premier" )
title.names<-c("CUIMC", "OPTUM",
               "Hospital CDM", "CCAE", "MDCD", "PanTher",  "PHD")
```

## Table 1: Characteristics of study participants

```{r , echo=FALSE}
load(paste0(final.figs_tables, "/table.1.Rdata"))

ft <- flextable(table.1) 
ft <- set_header_labels(ft,
    Characteristic = "", CUIMC = title.names[1],
    optum = title.names[2], CCAE = title.names[4], datamaster = title.names[3],
    mdcd=title.names[5], panther=title.names[6], premier=title.names[7])
autofit(ft)

```



##### break


## Table 2: In-hospital outcomes  

##### break



## Table 3: All-cause mortality at 30 and 180 days 

##### break

## Figure 1. ROC plot

##### break

## Figure 2. Calibration plot

##### break

# Appendix 

## Study inclusion flow charts

### CUIMC 
```{r}
include_graphics(file.path(working.figs_tables,
                     paste0(names[1],".inlusion1.png")))
```

##### break

### OPTUM 
```{r}
include_graphics(file.path(working.figs_tables,
                     paste0(names[2],".inlusion1.png")))
```

##### break 

### Hospital CDM 
```{r}
include_graphics(file.path(working.figs_tables,
                     paste0(names[3],".inlusion1.png")))
```

##### break

### CCAE 
```{r}
include_graphics(file.path(working.figs_tables,
                     paste0(names[4],".inlusion1.png")))
```

##### break

### MDCD 
```{r}
include_graphics(file.path(working.figs_tables,
                     paste0(names[5],".inlusion1.png")))
```

##### break

### PanTher 
```{r}
include_graphics(file.path(working.figs_tables,
                     paste0(names[6],".inlusion1.png")))
```
##### break

### Premier 
```{r}
include_graphics(file.path(working.figs_tables,
                     paste0(names[7],".inlusion1.png")))
```

##### break


## Comparison of characteristics of ECMO with ARDS cohort to all patients undergoing ECMO (aged 18 or older, and with at least 30 days of prior observation time)
### Appendix table 1 CUIMC patient characteristic:  ECMO with ARDS vs all ECMO 
```{r , echo=FALSE}
table.1.CUIMC.age_30.day_comparison<-read.csv2(unz(
             file.path(folder.table_1_output,
             paste0(names[1],"_plots_tables", ".zip")), 
             "table.1.age_30.day_comparison.csv"),
             col.names=c("Characteristic", "inc",  "all", "SMD"),
             stringsAsFactors = FALSE)
table.1.CUIMC.age_30.day_comparison <- flextable(table.1.CUIMC.age_30.day_comparison) 
table.1.CUIMC.age_30.day_comparison <- set_header_labels(table.1.CUIMC.age_30.day_comparison,
    Characteristic = "", inc = "CUIMC ECMO with ARDS",
    all = "CUIMC all ECMO", SMD = "SMD")
autofit(table.1.CUIMC.age_30.day_comparison)

```

##### break

### Appendix table 2 OPTUM patient characteristic:  ECMO with ARDS vs all ECMO 
```{r , echo=FALSE}
table.1.optum.age_30.day_comparison<-read.csv2(unz(
             file.path(folder.table_1_output,
             paste0(names[2],"_plots_tables", ".zip")), 
             "table.1.age_30.day_comparison.csv"),
             col.names=c("Characteristic", "inc",  "all", "SMD"),
             stringsAsFactors = FALSE)
table.1.optum.age_30.day_comparison <- flextable(table.1.optum.age_30.day_comparison) 
table.1.optum.age_30.day_comparison <- set_header_labels(table.1.optum.age_30.day_comparison,
    Characteristic = "", inc = "OPTUM ECMO with ARDS",
    all = "OPTUM all ECMO", SMD = "SMD")
autofit(table.1.optum.age_30.day_comparison)


```


##### break

### Appendix table 3 Hospital CDM patient characteristic:  ECMO with ARDS vs all ECMO 
```{r , echo=FALSE}
table.1.datamaster.age_30.day_comparison<-read.csv2(unz(
             file.path(folder.table_1_output,
             paste0(names[3],"_plots_tables", ".zip")), 
             "table.1.age_30.day_comparison.csv"),
             col.names=c("Characteristic", "inc",  "all", "SMD"),
             stringsAsFactors = FALSE)
table.1.datamaster.age_30.day_comparison <- flextable(table.1.datamaster.age_30.day_comparison) 
table.1.datamaster.age_30.day_comparison <- set_header_labels(table.1.datamaster.age_30.day_comparison,
    Characteristic = "", inc = "Hospital CDM ECMO with ARDS",
    all = "Hospital CDM all ECMO", SMD = "SMD")
knit_print(autofit(table.1.datamaster.age_30.day_comparison),
           ft.align="left")
             
             
             
            

```
### Appendix table 4 CCAE patient characteristic:  ECMO with ARDS vs all ECMO 
```{r , echo=FALSE}
table.1.ccae.age_30.day_comparison<-read.csv2(unz(
             file.path(folder.table_1_output,
             paste0(names[4],"_plots_tables", ".zip")), 
             "table.1.age_30.day_comparison.csv"),
             col.names=c("Characteristic", "inc",  "all", "SMD"),
             stringsAsFactors = FALSE)
table.1.ccae.age_30.day_comparison <- flextable(table.1.ccae.age_30.day_comparison) 
table.1.ccae.age_30.day_comparison <- set_header_labels(table.1.ccae.age_30.day_comparison,
    Characteristic = "", inc = "CCAE ECMO with ARDS",
    all = "CCAE all ECMO", SMD = "SMD")
autofit(table.1.ccae.age_30.day_comparison)


```


##### break

### Appendix table 5 MDCD patient characteristic:  ECMO with ARDS vs all ECMO 
```{r , echo=FALSE}
table.1.ccae.age_30.day_comparison<-read.csv2(unz(
             file.path(folder.table_1_output,
             paste0(names[5],"_plots_tables", ".zip")), 
             "table.1.age_30.day_comparison.csv"),
             col.names=c("Characteristic", "inc",  "all", "SMD"),
             stringsAsFactors = FALSE)
table.1.ccae.age_30.day_comparison <- flextable(table.1.ccae.age_30.day_comparison) 
table.1.ccae.age_30.day_comparison <- set_header_labels(table.1.ccae.age_30.day_comparison,
    Characteristic = "", inc = "MDCD ECMO with ARDS",
    all = "MDCD all ECMO", SMD = "SMD")
autofit(table.1.ccae.age_30.day_comparison)


```


##### break

### Appendix table 6 PanTher patient characteristic: ECMO with ARDS vs all ECMO 
```{r , echo=FALSE}
table.1.ccae.age_30.day_comparison<-read.csv2(unz(
             file.path(folder.table_1_output,
             paste0(names[6],"_plots_tables", ".zip")), 
             "table.1.age_30.day_comparison.csv"),
             col.names=c("Characteristic", "inc",  "all", "SMD"),
             stringsAsFactors = FALSE)
table.1.ccae.age_30.day_comparison <- flextable(table.1.ccae.age_30.day_comparison) 
table.1.ccae.age_30.day_comparison <- set_header_labels(table.1.ccae.age_30.day_comparison,
    Characteristic = "", inc = "PanTher ECMO with ARDS",
    all = "PanTher all ECMO", SMD = "SMD")
autofit(table.1.ccae.age_30.day_comparison)


```


##### break
